Distributed Behavior in a Fluid Analogy Architecture

### 2017-12-10 papers/draft.tex
Adds bibliography

%% Language and font encodings
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}

@@

%% Useful packages
\usepackage{listings}
\usepackage{amsmath}
\usepackage{pdfpages}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}

@@

        The below table summarizes the results of comparing each copycat-variant's distribution with each other copycat-variant.
        \includepdf[pages={-}]{resources/final.pdf}

@@

        [Summary of introduction, elaboration based on results]

@@

\bibliographystyle{alpha}
\bibliography{sample}

>>>>

@@

%% Useful packages
\usepackage{listings}
\usepackage{amsmath}
\usepackage{pdfpages}
\usepackage{graphicx}

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}

\usepackage[backend=biber,style=alphabetic,sorting=ynt]{biblatex}
\addbibresource{sources.bib}

\usepackage[colorinlistoftodos]{todonotes}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}

@@

        The below table summarizes the results of comparing each copycat-variant's distribution with each other copycat-variant.
        For the table, please see \href{"https://docs.google.com/spreadsheets/d/1d4EyEbWLJpLYlE7qSPPb8e1SqCAZUvtqVCd0Ns88E-8/edit?usp=sharing"}{google sheets}.

@@

        [Summary of introduction, elaboration based on results]
        Let's cite! The Einstein's journal paper \cite{einstein} and the Dirac's
        book \cite{dirac} are physics related items.

@@

\printbibliography
